---
title: "Campus 2 Canton App Overview"
output: github_document
---
# campus2canton-data
Public repo for campus2canton data

<!-- badges: start -->
<!-- badges: end -->

[![College Team App](https://github.com/JerrickBackous/college_team_analyzer/workflows/R-CMD-check/badge.svg)](https://github.com/JerrickBackous/college_team_analyzer/actions)
[![College Coach App](https://github.com/JerrickBackous/college_coach_analyzer/workflows/R-CMD-check/badge.svg)](https://github.com/JerrickBackous/college_coach_analyzer/actions)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo = FALSE, message = FALSE, warning = FALSE}

status <- tibble::tribble(
  ~Data, ~ Status,
  "campus2canton-data", "",
  "Player Metric App", "[![Player Metric App](https://github.com/JerrickBackous/metric_app/workflows/R-CMD-check/badge.svg)]",
  "Player Metric Table", "[![Player Metric Table](https://github.com/JerrickBackous/college_player_data_app/workflows/R-CMD-check/badge.svg)]"
  ) |> 
  dplyr::mutate_all(tidyr::replace_na,"")
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
knitr::kable(status)
```
## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
