---
title: "Campus 2 Canton App Overview"
output: github_document
---
# campus2canton-data
Public repo for campus2canton data

<!-- badges: start -->
[College Team App][![R-CMD-check](https://github.com/JerrickBackous/college_team_analyzer/workflows/R-CMD-check/badge.svg)](https://github.com/JerrickBackous/college_team_analyzer/actions)
<!-- badges: end -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
